MolProbity's Ultimate Rotamer-Library Distributions for Model Validation

### 2016-02-19 discussion.tex
Added a citation to Fitmunk which uses the Top500 contours

\subsection{Use of the Top8000 rotamer distributions in model building}
Although the Top8000 rotamer distributions were created specifically for MolProbity's validation of sidechain conformations, they also can be used in model building for crystallography, design, homology, etc., as the Top500 library has been \cite{Arendall2005, Langer2008, Emsley:ba5144, Headd2008, Terwilliger2008, Adams:2010fk, Gainza2013}. To make model building computationally tractable, \textcolor{red}{the procedure has usually been to} initially fit sidechains as discrete conformations at rotamer values, then to minimize or to test at neighboring sample points, using $\sigma$ to inform the allowable range for each $\chi$. However, most rotamer distributions are far from normal and often have quite complex shapes, as can be seen in Figures \ref{fig:AspAsn} and \ref{fig:outcontour}. Thus the approach of using a central value and $\sigma$ cannot adequately describe allowed sidechain conformations.

>>>>

\subsection{Use of the Top8000 rotamer distributions in model building}
Although the Top8000 rotamer distributions were created specifically for MolProbity's validation of sidechain conformations, they also can be used in model building for crystallography, design, homology, etc., as the Top500 library has been \cite{Arendall2005, Langer2008, Emsley:ba5144, Headd2008, Terwilliger2008, Adams:2010fk, Gainza2013,Porebski2016}. To make model building computationally tractable, \textcolor{red}{the procedure has usually been to} initially fit sidechains as discrete conformations at rotamer values, then to minimize or to test at neighboring sample points, using $\sigma$ to inform the allowable range for each $\chi$. However, most rotamer distributions are far from normal and often have quite complex shapes, as can be seen in Figures \ref{fig:AspAsn} and \ref{fig:outcontour}. Thus the approach of using a central value and $\sigma$ cannot adequately describe allowed sidechain conformations.
